---
title: "linear model from Web"
author: "iboni archie"
date: "summer 2021"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS

### scatterplot

```{r}
plot(SIMS~ARM,data=data)
```
In this scatter plot it showing us two numerical variables SIMS and ARM
we are looking to see how Sims affects ARM and if there is a realtionship between the two on the X axis we have SIMS and on the Y there is Arm. There is 
an up hill pattern to the right which shows a positive relationship between the two







### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```
The correlation explains a strong relationship between the two variables there when the the number is greater than 0.75 is considered strong The correlation between SIMS and ARM is 0.68 which is slightly under which leads us to believe that there is not a strong correlation between the two variables


### Inferential  (Build model.1)

  
```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

In the table the coefficents indicate the direction of the relationship between
a predicttor variable and its response variable.The range cannot be more that 1.0 or less that -1.0. Since the residual standard error is 1.2 which is closer to zero the variables are a closer fit the regression with a low residual standard error will have data points that are packed closely together. The adjsuted R squared being 0.4 suggest that is explainging that 40 % of the variables is are adding additional input and not much value to the model.




#### Predict at target point


#### scatterplot with model fit



```{r}
basicNN + geom_point() + geom_smooth(method=lm)
``` 

In this model we see that the line crossing through is the line that best fits 
showing us that the two variables relationship to one another with the dots faliing close to the line in a upward angel shows that there is a positive 
correlation between the two variables 










  

## Model 2 SIM~GRIP

### Now add in scatterplot

```{r}
plot(SIMS~GRIP,data=data)
```

In this scatterplot we are comparing Sims vs Grip vs Sims vs Arm. This model is showing that there is still in upward relationship but with less correlation as the dots are more spaced out than the previous model which can be lead to believe that there is less an relationship betweent these two varaibles





### Numerical results 

```{r}
cor(SIMS~GRIP,data=data)
```
The correlation for Sims and Grip is 0.63 63% this numerical value is stating that the two variables realtionships in this model have less of a realtionship
to one another compared to Sims vs Arm the numerical value has gone down.





### Inferential  (Build model.2)
 
```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```
 In this table the coefficents indicate the direction of the realtioship between a predictor variable and its response variable  the residual standard error is 1.29 has gone up meaning showing that there is a gap between the relationship of the two variables the adjusted R squared is 0.     which is lower than the previous model which indicates that the new variable GRIP is not addin any value to this model.The p value is less than 2.2 indicating we should reject the null hypothesis
 


#### predict model.2 at target point

#### now add the model fit to our plot for model.2
  








## Model 3 SIM~ARM+GRIP

### Numerical results (cor)

`
  
### Inferential  (Build 2-dimentional model.3)

```{r}
model.3 <- lm(SIMS~ARM + GRIP,data=data)
summary.lm(model.3)
```











#### predict model.3 at target point
  

## Comparing nested models ANOVA Test

### Model.1 vs Model.3
### Model.2 vs Model.3

## Informally compare Model.1 with model.2

